Bitmap Indexing for Fast Analysis of Large Datasets

### 2016-03-28 ms/ms.tex
yt ref

These procedures were implemented as part of the {\tt yt} python package \addref in order to facilitate the analysis of large astrophysical N-body simulations. The open source EWAHBoolArray c++ package is used for implementing EWAH bitmaps \citep{Lemire2010,Kaser2016}.
\todo{more/separate code section...?}

>>>>

These procedures were implemented as part of the {\tt yt} python package \citep{Turk20d11a} in order to facilitate the analysis of large astrophysical N-body simulations. The open source EWAHBoolArray C++ package is used for implementing EWAH bitmaps \citep{Lemire2010,Kaser2016}.
\todo{more/separate code section...?}
